---
title: "warmup03-jacob-yeung"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(psych)

```
The data have a header containing the variable names.
The vaues are separated by a comma.
There are missing values. They are codified by "".

```{r}
#1 Importing Data

github = 'https://raw.githubusercontent.com/ucb-stat133/stat133-hws/'
repo = 'master/data/nba2018-players.csv'
datafile = paste0(github, repo)

#a.
data_types = c("character", "factor", "factor", "integer", "integer", "integer", "integer", "character", "real", "integer", "integer", "integer", "integer", "integer", "integer")

#b.
nba = read.csv(datafile, header = TRUE, colClasses = data_types)
str(nba, vec.len = 1)
nba1 = nba
#c.
nba2 = read.table(datafile, header = TRUE, sep = ",", colClasses = data_types)
str(nba2, vec.len = 1)

#d.
identical(nba, nba2)

salary = nba$salary
```
2
a.  
The first 10 rows are the first 9 rows of nba with the headers of nba as the first row. The column names are now V1,..., V15.

b.
All the columns are now factors.

c.
It fails to import the data because the command is missing an element in the argument, namely header.

d.
Importing the data with specifying the data types uses less memory than without specifying the data types.

e.
All the data values become characters.

```{r}
#3a. Examine Salary
describe(nba$salary)
salary = nba$salary
#b.
hist(nba$salary, xlim = range(nba$salary))

#c.
nba$salary2 = nba$salary / 1000000
hist(nba$salary2)
nba1$salary = salary
#d.
nba$salary2 = log(nba$salary2)
hist(nba$salary2)
#The histogram is more symmetrically distributed. The histogram is more right skewed now, with more values on the right half of the histogram.

#e.
low = nba$salary2 < -3
length(less[less == TRUE])
#8 players

#f.
nba[nba$salary2 < -3, c("player", "weight", "height", "team", "position")]

#g.
nba = nba[low, ]
dim(nba)
```

```{r}
#4a
describe(nba1$points)
hist(nba1$points)
#b.
p = nba1$points == 0
nba1$points[p] = 0.1
hist(log(nba1$points))

#The points are again changing from having majority of points onthe left to having majority of points on the left. The plot has many points around the 5-6 values for the log transformed points.
```

```{r}
#5 Transforming Age into a Factor
salary2 = nba$salary2
#a.
boxplot(salary2 ~ nba$age, data = nba1, xlab = "Age", ylab = "Salary (in millions)")
#The hightest median salaries seem to occur around 31 years of age.The players younger than 25 seem to have much lower median salaries.

#b.
boxplot(nba1$points ~ age, data = nba1, xlab = "Age", ylab = "Points")

#The players around 27 years of age seem to have the highest median scores. From around age 30 to age 34, players seems to have approximately the same median scores.

#c.
age20 = nba1$age < 20
nba1$age2 = nba1$age
nba1$age2[age20] = 20
age2 = cut(nba1$age2, breaks = c(19, 24, 29, Inf), labels = c("20-24", "25-29", "30+"))
nba1$age2 = age2
summary(age2)
```

```{r}
#6 Salary vs Points, by Age Group

#a.
palette1 = c("#D4D62A", "#4F9D66", "#9575AB")

#b.
age_colors1 = age2 == "20-24"
age_colors2 = age2 == "25-29"
age_colors3 = age2 == "30+"
age_colors = age2

# for (x in 1:length(nba1$age2)){
#   if(nba1$age2[x] == "20-24"){
#     nba1$age2[x] = factor(palette1[1])
#   }
#   else if(nba1$age2[x] == "25-29"){
#     nba1$age2[x] = factor(palette1[2])
#   }
#   else {
#     nba1$age2[x] = factor(palette1[3])
#   }
# }
# 
# #c
# plot(nba1$salary ~ nba1$points, data = nba1, log = "xy", main = "", xlab = "Points (log scale)", ylab = "Salary (log $)", col = age_colors, pch = 19, cex = 0.6)
# legend("bottomright", fill = palette1, legned = levels(age2), title = "Age Groups", cex = 0.8)
```

```{r}
#7
#a.
boxplot(nba$salary2 ~ nba$position, data = nba1, xlab = "Positions", ylab = "Log(Salary)")
# There is no large difference in salary depending on position of players.

#b.
boxplot(nba1$points ~ position, data = nba1, xlab = "Positions", ylab = "Points")
#There isn't a large difference in scored points based on position. However, shooting guards have the highest median of points scored.

```
















