---
title: "Lab 3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

"The character delimiter is a comma.  
There is not a row for column names.  
There are no missing values.  
Sex - character  
Length - continuous  
Diameter - continuous  
Height - continuous  
Whole weight - continuous  
Shucked weight - continuous  
Viscera weight - continuous  
Shell weight - continuous  
Rings - integer  "

```{r}
url = "http://archive.ics.uci.edu/ml/machine-learning-databases/abalone/abalone.data"
abalone = read.table(url, sep = ",")
column_names = c("Sex", "Length", "Diameter", "Height", "Whole", "Shucked", "Viscera", "Shell", "Rings")
column_types = c("character", "double", "double", "double", "double", "double", "double", "double", "integer")
abalone = read.table("abalone.data", header = FALSE, sep = ",", col.names = column_names, colClasses = column_types)
str(abalone)
abalone2 = read.csv(url)
str(abalone2)
abalone10 = read.csv(url, nrows = 10)
str(abalone10)
abalone20 = read.table(url, sep = ",", skip = 10, nrows = 10)
str(abalone20)
```

"When a column has value \"NULL\", the colmmn is skipped."

```{r}
library(psych)
abalone_no_sex = abalone[-grep('Sex', colnames(abalone))]
describe(abalone)

```

```{r}
five_rows = abalone[1:5, ]
every_five = abalone[seq(1, length(abalone), 5)]
last_five = abalone[(nrow(abalone) - 4):(nrow(abalone)), ]
height14 = abalone[abalone$Height < 0.14, ]
dim(height14)
infant = abalone[abalone$Sex == "I", ]
dim(infant)
male_female = abalone[abalone$Sex != "I", ]
dim(male_female)
rings25 = abalone[abalone$Rings > 25, c("Sex", "Rings")]
infant_rings = abalone[abalone$Sex == "I" & 3 < abalone$Rings & abalone$Rings < 6, c("Sex", "Rings", "Diameter")]
```

```{r}
#Adding New Variables and Sorting Rows
abies = abalone[abalone$Sex == 'I', c('Length', 'Height', 'Diameter')]
abies$Ht_Len = abies$Height / abies$Length
abies2 = abies[order(abies$Length, decreasing = TRUE), ]
abies$product = abies$Length * abies$Height
abies3 = abies
abies3$log_height = log(abies$Height)
abies3$log_length = log(abies$Length)
abalone12 = abalone[abalone$Height < 0.12, ]
abalone12 = abalone[order(abalone$Height, decreasing = FALSE), ]
abalone_high = abalone12[(nrow(abalone) - 4):nrow(abalone12), c("Sex", "Diameter", "Rings")]
abalone_long = abalone[order(abalone$Length, decreasing = TRUE), ]
abalone_long = abalone_long[(1:5), c("Sex", "Diameter", "Rings")]


```
```{r}
#Plot Behaviors

plot(abalone$Height)
#Returns a scatterplot with height on the y axis and index of the abalone on the x axis

Sex = factor(abalone$Sex)
#Returns a barplot of the frequencies of each sex

plot(abalone$Height, abalone$Length)
#Returns a scatterplot with abalone$Length on the y axis and abalone$Height on the x axis

HL = abalone[, c("Height", "Length")]
plot(HL)
#Returns a scatterplot with Length on the y axis and Height on the x axis

HLD = abalone[, c("Height", "Length", "Diameter")]
plot(HLD)  
```
  
Returns 6 ((number of numeric columns)$^2$ - number of numeric columns) graphs, with each graph a scatterplot compared to one other numeric

```{r}
sex_length = data.frame(Sex, abalone$Length)
plot(sex_length)
#Returns 3 box plots, one for each sex

length_sex = data.frame(abalone$Length, Sex)
plot(length_sex)
#Returns a scatter plot with abalone.Length on the x axis and sex(denoted as female = 1.0, infant = 2.0, male = 3.0) on the y axis
```
```{r}
#Scatter Diagrams
par(mfcol = c(2, 2))
plot(sex_length, main = "Abalone Lengths for Corresponding Sex", xlab = "Sex", ylab = "Length", sub = "Box Plot", col = "red")
plot(HL, main = "Abalone Heights vs Lengths", xlab = "Height", ylab = "Length", col = "blue", pch = 1)
plot(log(HL), main = "Abalone Heights vs Lengths (Logarithmic Transformation Applied)", cex = 1)
boxplot(HL, main = "Abalone Heights and Lengths Each in Boxplot", ylab = "Inches")

```





















