---
title: "warmup02-jacob-yeung"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plyr)
```
```{r}
#1 Vectors

number = c(30L, 35L, 23L, 9L, 11L, 27L, 34L, 6L, 3L, 0L)
player = c("Stephen Curry", "Kevin Durant", "Draymond Green", "Andre Iguodala", "Klay Thompson", "Zaza Pachulia", "Shaun Livingston", "Nick Young", "David West", "Patrick McCaw")
position = factor(c("PG", "PF", "PF", "SF", "SG", "C", "PG", "SG", "C", "SG"))
height = c("6-3", "6-9", "6-7", "6-6", "6-7", "6-11", "6-7", "6-7", "6-9", "6-7")
weight = c(190, 240, 230, 215, 215, 270, 192, 210, 250, 185)
birthdate = c("March 14, 1988", "September 29, 1988", "March 4, 1990", "January 28, 1984", "February 8, 1990", "February 10, 1984", "September 11, 1985", "June 1, 1985", "August 29, 1980", "October 25, 1995")
experience = c(8L, 10L, 5L, 13L, 6L, 14L, 12L, 10L, 14L, 1L)
college = c("Davidson College", "University of Texas at Austin", "Michigan State University", "University of Arizona", "Washington State University", "NA", "NA", "University of Southern California", "Xavier University", "University of Nevada, Las Vegas")

#a Heaviest Player
player_info = data.frame(player, number, position, height, weight, birthdate, experience, college)
heavy_first = player_info[order(player_info$weight, decreasing = TRUE), ]
heavy_first$player[1]

#b 6-6 College
player_info[(player_info$height == "6-6"), "college"]

#c Most experienced
dec_exp = player_info[order(player_info$experience, decreasing = TRUE), ]
dec_exp$position[1:2]

#d Lightest Player
heavy_first$number[nrow(heavy_first)]

#e Frequencies of Position Values
count(position)

#f Weight above Average
length(heavy_first[heavy_first$weight > mean(heavy_first$weight), "weight"])

#g 9-12 years of experience
length(player_info[9 <= player_info$experience & player_info$experience <= 12, "player"])

#h Mean Years of Experience
mean(player_info[player_info$position == "SG", "experience"])

#i Median Weight
median(player_info[player_info$position != "C", "weight"])

#j First Quartile of Years of Experience
quantile(player_info[player_info$position == "SG" | player_info$position == "PF", "experience"])[2]
```

```{r}
#2 List for GSW
gsw <- list(
  player = player,
  number = number,
  position = position,
  weight = weight,
  experience = experience
)

#a Heaviest Player Number
gsw$player[which(gsw$weight == max(gsw$weight))]

#b Less Experience
gsw$position[which(gsw$experience == min(gsw$experience))]

#c Experience
length(gsw$player[gsw$experience < 8 | gsw$experience > 11])

#d Third Quartile
quantile(gsw$experience[gsw$position == "PF" | gsw$position == "SG"])[4]

#e Furthest Weight
gsw$player[which(max(abs(gsw$weight - mean(gsw$weight))) + mean(gsw$weight) == gsw$weight)]
```
```{r}
#3 More Lists
hp <- list(
  first = 'Harry',
  last = 'Potter',
  courses = c('Potions', 'Enchantments', 'Spells'),
  sport = 'quidditch',
  age = 18L,
  gpa = 3.9
)

#a
class(hp)

#b
length(hp)

#c
length(hp$courses)

#d
typeof(hp$age)

#e
typeof(hp$gpa)

#f
combine = hp[c("age", "gpa")]
typeof(combine)
#returns a list
```
#4 Technical Questions  
  
a. The command returns 2 because TRUE is mapped to 1L.  
b. FALSE because the negative sign in front of the 2 values the "-2" as false.
c. Command A has the numeric first and addition, coercing the !TRUE into an integer. Likewise, Command B has !TRUE first, causing the statement to go to FALSE.  

```{r}
#5
lord <- c('v', 'o', 'l', 'd', 'e', 'm', 'o', 'r', 't')
```
a. lord[TRUE]
The vector is getting recycled, so each element in lord is assigned TRUE.

b. lord[length(lord) + 1]
The index is out of bounds, so returns NA.

c. lord[seq(from = length(lord), to = 1, by = -2)]
The command extracts every other element from lord, backwards, until it reaches the first index.

d. lord[lord == "o"]
The command is filtering out all the elements in lord that are not "o". Subsetting all the other elements.

e. lord[lord != "e" & lord != "o"]
The command is filtering out all the elements in lord that are equivalent to "e" and "o". Subsetting all the other elements.

f. lord[lord %in% c('a', 'e', 'i', 'o', 'u')]
The command is filtering out all the elements in lord that are not in 'a', 'e', 'i', 'o', 'u'. Subsetting all the other elements.

g. toupper(lord[!(lord %in% c('a', 'e', 'i', 'o', 'u'))])
The command is filtering out all the elements in lord that are in 'a', 'e', 'i', 'o', 'u' and then upper casing the remaining elements. Subsetting all the other elements.

h. paste(lord, collapse = '')
The command is filtering out the white spaces when lord is returned.

i. lord[is.na(lord)]
The command is trying to subset lord by taking all the NA values in lord.

j. sum(!is.na(lord))
The command subsetted all the elements in lord that are not NA in value and summed up their truth values.

```{r}
#6
vol = matrix(lord, nrow = 3, ncol = 3)

#a
vol[1, ]

#b
vol[1:2 , c(2, 1)]

#c
vol[c(3, 2, 1), ]

#d
vol[, c(1, 2, 2)]

#e
vol[c(3, 2, 1), c(3, 2, 1)]

#f
vol[c(3, 2, 1, 1, 2, 3), c(3, 2, 2, 3)]

#g
vol[c(3, 2, 1, 1, 2, 3), c(1, 2, 3, 3, 2, 1)]
```














